Jonathan Carbonneau
I pledge my honor that I have abided by the Stevens Honor System
Problem 1
```{r}
library(moments)
n = c(20,30,50,75,100)
Binomial  <- c()
#calculated using the laplace function.
laplaceDistro <- c(0.54542,0.0811,0.000347,1.47587E-7,7.5739881E-11) 


for (i in n){
Binomial  <- append(Binomial , pbinom(8.75, i, 0.4))
}

plot(Binomial , main="Binomial Distrabution") 
plot(laplaceDistro, main="Laplace Distrabution") 
plot(abs(Binomial-laplaceDistro), main="Errors of all approximations") 

input <- c(70,77,68,69,84,80,75,65,76,78,82)

boxplot(input)
points(mean(input),col="red", pch = 19)
points(min(input),col="red", pch = 19)
points(max(input),col="red", pch = 19)

skewness(rnorm(100000000, mean(input), var(input))) 

```
iii
Error
``` {r}
abs(Binomial-laplaceDistro)

```
The Laplace distribution is fairly accurate

iv
As the number of samples increases the error decrees logarithmicly


```{r}
twoia <- c()
twoib <- c()
n <- 20
for (i in 1:100){
x<-rnorm(n,2,9)
twoia <- append(twoia,((mean(x) -2)/sqrt(3^2/n)))
twoib <- append(twoib,((n-2)*var(x))/sqrt(3^2))
}
 plot(density(twoia), main="n = 20 for (x-2)/sqrt(3^2/n)")
 plot(density(twoib), main="n = 20 for ((n-2)*9)/sqrt(3^2)")
 plot(twoia , twoib, main="n = 20 for ((mean(x) -2)/sqrt(3^2/n),((n-2)*var(x))/sqrt(3^2)")

 twoiia <- c()
 twoiib <- c()
 n <- 30
 for (i in 1:100){
 x<-rnorm(n,2,9)
 twoiia<- append(twoiia,(mean(x)-2)/sqrt(3^2/n))
 twoiib <- append(twoiib,((n-2)*var(x))/sqrt(3^2))
}
plot(density(twoiia), main="n = 30 for (x-2)/sqrt(3^2/n)")
plot(density(twoiib), main="n = 30 for ((n-2)*9)/sqrt(3^2)")
plot(twoiia , twoiib, main="n = 30 for ((mean(x) -2)/sqrt(3^2/n),((n-2)*var(x))/sqrt(3^2)")

twoiiia <- c()
twoiiib <- c()
n <- 50
for (i in 1:100){
x<-rnorm(n,2,9)
twoiiia<- append(twoiiia,((mean(x)-2)/sqrt(3^2/n)))
twoiiib <- append(twoiiib,((n-2)*var(x))/sqrt(3^2))
}
plot(density(twoiiia), main="n = 50 for (x-2)/sqrt(3^2/n)")
plot(density(twoiiib), main="n = 50 for ((n-2)*9)/sqrt(3^2)")
plot(twoiiia , twoiiib, main="n = 50 for ((mean(x) -2)/sqrt(3^2/n),((n-2)*var(x))/sqrt(3^2)")
twoiiiia <- c()
twoiiiib <- c()
n <- 75
for (i in 1:100){
x<-rnorm(n,2,9)
twoiiiia<- append(twoiiiia,(mean(x)-2)/sqrt(3^2/n))
twoiiiib <- append(twoiiiib,((n-2)*var(x))/sqrt(3^2))
}
plot(density(twoiiiia), main="n = 75 for (x-2)/sqrt(3^2/n)")
plot(density(twoiiiib), main="n = 75 for ((n-2)*9)/sqrt(3^2)")
plot(twoiiiia , twoiiiib, main="n = 75 for ((mean(x) -2)/sqrt(3^2/n),((n-2)*var(x))/sqrt(3^2)")

```
v
As the sample size n increases the probability distribution curve becomes more normal

vi
based on the probability curves and the scatter plot one can guess that the functions are corolated
